DTOADQ

### 2017-09-29 documentation/paper.tex
adding documentation, partially implementing contributions/weights

\message{ !name(paper.tex)}\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{color}
\usepackage[margin=1.15in]{geometry}

@@

\begin{document}

\message{ !name(paper.tex) !offset(-3) }

  \maketitle
  \section{Introduction}
    I apologize for this being very lengthy and at times mathematically heavy,
    but there is no way of avoiding it.

@@

    And now
  \begin{align}
    F = \Sigma_s\Sigma_t \alpha^L_s c_{s, t} \alpha^E_t
  \end{align}
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      \frac{L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | \frac{W^0_e(z_0)}{p_A(z_0)},
      &i = 1,\\
      (\frac{f_s(y_{i+1} \rightarrow y_i \rightarrow y_{i-1})}{p_{\sigma}(y_i
      \rightarrow y_{i-1})} | \frac{f_s(z_{i-1} \rightarrow z_{i-2} \rightarrow
      z_{i-3}}{p_\sigma(z_{i-2} \rightarrow z_{i-1})}) \alpha^{L|E}_{i-1},
      &i > 1
    \end{cases}
  \end{align}
    There is no case for $i = 0$ as either, the path doesn't exist, or if one
    does exist, $y_0$ and $z_0$ do not contribute to the image. Veach (and many other
    sources), leave this in, but it's unnecessary and can be confusing. However,
    there may be cases where $s = 0$ ($t = 0$ is not possible without a
    physical camera lens), which is equivalent to just forward path tracing.
    Well, in either case where both paths exist or only the camera path exists,
    the connection strategy below describes how to connect the edges of the two
    paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 0,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s = s, t > 0
    \end{cases}
  \end{align}
    One immediately obvious optimization that could be made with this model is
    in regards to the visibility check in the geometric term, if you were to
    expand $I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be
    cancelled out for the entire equation, except for the connection term $c$.
    The expansion is not shown as it is very lengthy, and unnecessary. Paths
    $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ being
    visible is intuitively obvious as we are already generating these paths.
    Specifically, the definition of $V$ is
  \begin{align}
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
  \end{align}
    where $m$ is a march through the SDF map. Since the paths are being
    generated using march. A visibility check is only necessary for the
    connection edge
    \begin{align*}
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 
    \end{align*}
\\
    Moving on, for $\alpha^{L|E}_i$, these are equivalent for both $L$ and $E$,
    the problem is that the $\bar{y}$ path is generated in perspective of the
    light source, so we have to call the BSDF in perspective of the camera; the
    path is flipped. Handling $\bar{y}$ is significantly easier than $\bar{z}$,
    as $\bar{y}$ is precomputed. For $\bar{z}$, the next vertex $z_{+1}$
    ($\omega_o$ in the perspective of SA), is unknown. For example $\alpha^L_1$
    in OpenCL looks like:

@@

\message{ !name(paper.tex) !offset(-368) }

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{color}
\usepackage[margin=1.15in]{geometry}

@@

\begin{document}
  \maketitle
  \section{Introduction}
    I apologize for this being very lengthy and at times mathematically heavy,
    but there is no way of avoiding it.

@@

    And now
  \begin{align}
    F = \Sigma_s\Sigma_t \alpha^L_s c_{s, t} \alpha^E_t
  \end{align}
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      \frac{L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | \frac{W^0_e(z_0)}{p_A(z_0)},
      &i = 1,\\
      (\frac{f_s(y_{i+1} \rightarrow y_i \rightarrow y_{i-1})}{p_{\sigma}(y_i
      \rightarrow y_{i-1})} | \frac{f_s(z_{i-1} \rightarrow z_{i-2} \rightarrow
      z_{i-3}}{p_\sigma(z_{i-2} \rightarrow z_{i-1})}) \alpha^{L|E}_{i-1},
      &i > 1
    \end{cases}
  \end{align}
    There is no case for $i = 0$ as either, the path doesn't exist, or if one
    does exist, $y_0$ and $z_0$ do not contribute to the image. Veach (and many other
    sources), leave this in, but it's unnecessarily confusing. A special case
    needs to be handled, unfortunately, for $\alpha^E_0$ as it is being
    generated on the fly while $\bar{z}$ is being constructed. The two options
    is to unroll the first iteration of the construction loop, or just allow the
    special case to exist. The latter is the better choice, as all kernels will
    enter and exit the special case at the same time, and the GPU might just
    unroll the loop anyways.
    There may be cases where $s = 0$ ($t = 0$ is not possible without a
    physical camera lens), which is equivalent to just forward path tracing.
    Well, in either case where both paths exist or only the camera path exists,
    the connection strategy below describes how to connect the edges of the two
    paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 0,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s = s, t > 0
    \end{cases}
  \end{align}
    One immediately obvious optimization that could be made with this model is
    in regards to the visibility check in the geometric term, if you were to
    expand $I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be
    cancelled out for the entire equation, except for the connection term $c$.
    The expansion is not shown as it is very lengthy, and unnecessary. Paths
    $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ being
    visible is intuitively obvious as the paths have been generated using the
    same technique used to check for visibility; raymarching. Specifically, the
    definition of $V$ is
  \begin{align}
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
  \end{align}
    where $m$ is a march through the SDF map. A visibility check is only
    necessary for the connection edge
    \begin{align*}
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 
    \end{align*}
\\
    Moving on, for $\alpha^{L|E}_i$, these are equivalent for both $L$ and $E$,
    the problem is that the $\bar{y}$ path is generated in perspective of the
    light source, so we have to call the BSDF in perspective of the camera; the
    path is flipped. Handling $\bar{y}$ is significantly easier than $\bar{z}$,
    as $\bar{y}$ is precomputed. For $\bar{z}$, the next vertex $z_{+1}$
    ($\omega_o$ in the perspective of SA), is unknown. For example $\alpha^L_1$
    in OpenCL looks like:

@@
